---
title: "Penguins ANOVA"
author: "Sandro Lallas"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read-in penguins.csv data

```{r, include = FALSE}

library("tidyverse")
library("car")
library("onewaytests")

penguins <- read_csv("penguins.csv")

```

Is there a significant difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, and Adelie)?

2. Do some exploring

New functions: with + table for easy counting over multiple factors

Update species name using case_when


```{r}

counts <- with(penguins, table(species, sex))

penguins2 <- penguins %>%
  mutate(common_name =
           case_when(
             species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
           )
         ) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")
  

```

- Exploratory graphs
- Summary statistics
- Levene's tests for equal variances
- one way ANOVA
- post-hoc testing

```{r}

hists <- ggplot(penguins2, aes(x = flipper_length)) +
  geom_histogram(aes(fill = common_name)) +
  facet_wrap(~common_name)

hists

qqs <- ggplot(penguins2, aes(sample = flipper_length)) +
  geom_qq() +
  facet_wrap(~common_name)

qqs

# Levene's test for equal variances (>2 groups... if you have two groups, use the F-test for equal variances)

# We'll use the function leveneTest from the 'car' package

# H0: Variances are equal
# HA: Variances are unequal

penguin_levene <- leveneTest(flipper_length ~ common_name, data = penguins2)

penguin_levene

# We retain the null hypothesis of equal variances (p = 0.06)

variances <- penguins2 %>% 
  group_by(common_name) %>% 
  summarize(
    variance = var(flipper_length)
  )

variances

```

