---
title: "Penguins ANOVA"
author: "Sandro Lallas"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read-in penguins.csv data

```{r, include = FALSE}

library("tidyverse")
library("car")
library("onewaytests")

penguins <- read_csv("penguins.csv")

```

Is there a significant difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, and Adelie)?

2. Do some exploring

New functions: with + table for easy counting over multiple factors

Update species name using case_when


```{r}

counts <- with(penguins, table(species, sex))

penguins2 <- penguins %>%
  mutate(common_name =
           case_when(
             species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
           )
         ) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")
  

```

- Exploratory graphs
- Summary statistics
- Levene's tests for equal variances
- One way ANOVA
-
